---
output:
  md_document:
    variant: markdown_github
csl: inst/bib_style.csl
---

# viewinteract: an R package for generating rules capturing cross-view interactions

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/README-figures/README-",
  dpi = 124
)
```

The main function is `get_rules()`. It takes a list of views as input; it outputs a list containing two matrices of 0-1 coded indicator variables (`rules_main`, which contains single-condition rules, that is: main effects; `rules_interact`, which contains two-condition rules for capturing cross-view interactions) and `dictionary`, which provides the conditions of the rules in the two matrices. 

## Example: Generating rules for two views of airquality data

We first create a list of two views of the same observations from the airquality data:

```{r, results = FALSE}
viewA <- na.omit(airquality)[-1]
viewB <- log(viewA)
views <- list(viewA, viewB)
```

As the package currently supports only binary factor response variables, we create such a response variables. Note that the first level should correspond to the target class:

```{r}
y <- na.omit(airquality)$Ozone
y <- factor(y < median(y))
levels(y) <- c("high", "low")
```

Now we use the `get_rules()` function to generate two new views: one containing main effects, one containing cross-view interactions. Note that the rule generation process involves random sampling of views and observations, so we first have to set the random seed:

```{r}
library("viewinteract")
set.seed(42)
new_views <- get_rules(views = views, y = y)
```

The result is a list with three objects: matrices `rules_main` and `ruleS_interact` and a dataframe `dictionary`. The two matrices contain 0-1 coded indicator variables for different sets of rules, for the same number of observations:

```{r}
dim(new_views$rules_main)
dim(new_views$rules_interact)
```

For example, the first three single-condition rules for the first six observations look as follows:

```{r}
new_views$rules_main[1:6, 1:3]
```

Similarly, the first three two-condition rules for the first six observations look as follows:

```{r}
new_views$rules_interact[1:6, 1:3]
```

The `dictionary` shows the conditions for each rule in `rules_main` and `rules_interact`:

```{r}
head(new_views$dictionary, n = 8L)
```


## Work to do

- When gradient boosting is not employed (i.e., `learnrate = 0`), perfectly pure nodes will yield an error
- Rules that are perfectly negatively correlated (i.e., yield the exact opposite 0-1 pattern) should be identified and eliminated.
